---
title: "analysis markdown"
author: "Thomas Schindler"
date: "21 November 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Thomas Analysis of Summer School' 2017 Data
Here I focus on data analysis sampled during Summer School 2017 in Agali forest.
Any collected data belong to greenhouse gas emissions by grey alder stems during the experiment phase. Basically, the experiment consisted of three periods - before, during, and afterartificial irrigation of the forest.

## Libraries to load
library(tidyverse)
library(ggthemes)
library(xtable)
library(ggplot2)
library(dplyr)

## Basic Steps

# Data Import,
# Select my file and read data into 'dat' dataframe
```{r}
dat<- read.csv("n2oR.csv", header = TRUE)
```

# Check Table View

```{r}
  head(dat)
```

# Data Validation (format numeric)
```{r}
str(dat)
```


# Initial Plot,  x - date, y - fluxes of the different trees and heights
```{r}
  hist(dat$Tree3h0)
```

# another basic plot option to see what happens
```{r}
```




## Check for Normal distribution
## Boxplots over time 
## Plots according to extra data: humidity and temperature, regression
