---
title: "R Notebook"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Thomas Analysis of Summer School' 2017 Data
Here I focus on data analysis sampled during Summer School 2017 in Agali forest.
Any collected data belong to greenhouse gas emissions by grey alder stems during the experiment phase. Basically, the experiment consisted of three periods - before, during, and afterartificial irrigation of the forest.

## Libraries to load
library(tidyverse)
library(tidyr)
library(ggthemes)
library(xtable)
library(ggplot2)
library(dplyr)
library(stringr)

## Basic Steps

# Data Import,
# Select my file and read data into 'dat' dataframe
```{r}
dat<- read.csv("n2oR.csv", header = TRUE)
```

# Check Table View

```{r}
  head(dat)
```

# Data are still in wrong format (wide instead of long)
# Thus, original data table needs to be converted /gathered - library 'tidyr' to be added to library list at the beginning

# The arguments to gather():
# - data: Data object
# - key: Name of new key column (made from names of data columns)
# - value: Name of new value column
# - ...: Names of source columns that contain values
# - factor_key: Treat the new key column as a factor (instead of character vector)

```{r}
  dat_long <- gather(dat, chamber, flux, Tree1ho:Tree12h170, factor_key=TRUE)
dat_long

```



# Data Validation (format numeric)
```{r}
str(dat)
```



## STILL TO DO
## Check for Normal distribution
## T-test
## Boxplots over time 
## Plots according to extra data: humidity and temperature, regression
