---
title: "Thomas Analysis"
author: "Thomas Schindler"
date: "29 November 2017"
output:   
    revealjs::revealjs_presentation:
    theme: moon
    incremental: true
    center: true
    fig_width: 7
    fig_height: 6
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

---

## Background

Here I focus on data analysis sampled during Summer School 2017 in Agali forest.
Any collected data belong to greenhouse gas emissions by grey alder stems during the experiment phase. Basically, the experiment consisted of three periods - before, during, and afterartificial irrigation of the forest. There are two groups of stem chambers, one located at the irrigation area (Tree 01 - 08, 12), the control group consists of trees 09-11. Further, the stem chambers are located on three heights. Exceptions are made at trees: 01, 05, 07, and 10 where chambers are situated at the bottom level only.

---

## Libraries to load

```{r Libraries, echo=TRUE, message=FALSE, warning=FALSE}
library(tidyverse)
library(tidyr)
library(ggthemes)
library(xtable)
library(ggplot2)
library(stringr)
library(scales)
library(cowplot)
library(Rmisc)
library(dplyr)
```

---

## N2O Data Import

- Select my file and read data into 'dat' dataframe
- File contains N20 fluxes for the SummerSchool irrigation experiment only.
- For extended time slots, another file (see below) will be used.

---

```{r Data Input}
dat<- read.csv("n2oR.csv", header = TRUE)
```

---
```{r}
dat
```

---

## Data are still in wrong format (wide instead of long)

Thus, original data table needs to be converted /gathered - library 'tidyr' to be added to library list at the beginning

The arguments to gather():
- data: Data object
- key: Name of new key column (made from names of data columns)
- value: Name of new value column
- ...: Names of source columns that contain values
- factor_key: Treat the new key column as a factor (instead of character vector)

---

### Re-Organising Data Colums, experimental sites

Zero level, experimental site
```{r, echo=TRUE}
  n2o0 <- gather(dat, "olevel", "flux", Tree1h0:Tree12h0, factor_key=TRUE)
```

---

```{r}
n2o0
```

---

80cm Level, experimental site
```{r}
  n2o80 <- gather(dat, "80level", "flux", Tree2h80:Tree12h80, factor_key=TRUE)
```

--- 
```{r}
n2o80
```

---

170cm Level, experimental site
```{r}
  n2o170 <- gather(dat, "170level", "flux", Tree2h170:Tree12h170, factor_key=TRUE)
```

---

```{r}
n2o170
```

---

## Re-Organising Data Colums, control sites

```{r}
  n2o0c <- gather(dat, "olevelC", "flux", Tree9h0:Tree11h0, factor_key=TRUE)
```

---

```{r}
n2o0c
```

---

80cm Level, experimental site
```{r}
  n2o80c <- gather(dat, "80levelC", "flux", Tree9h80:Tree11h80, factor_key=TRUE)
```

---

```{r}
  n2o80c
```

---

170cm Level, experimental site
```{r}
  n2o170c <- gather(dat, "170levelC", "flux", Tree9h170:Tree11h170, factor_key=TRUE)
```

---

```{r}
n2o170c
```

---

## ! Data now look much better

---

## N2O Boxplots from Experimental Site, no control spots, Level 0/80/170 cm

---

```{r}
  e1 <- ggplot(n2o0, 
              aes(x=Sampled,
                  y=flux))
  e1 <- e1 + 
        geom_boxplot(fill="blue", alpha=0.2) + 
          ggtitle("N2O, Level 0cm") +
          labs(x="Sampling Dates", y="N2O flux") +
          theme(plot.title = element_text(family = "Trebuchet MS", color="#666666", face="bold", size=18, hjust=0)) +
          theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
          scale_y_continuous(name="flux in myg/m-2 h-1", limits=c(0, 20)) 
```

---

```{r N2OExp0level, echo=FALSE, message=FALSE, warning=FALSE}
  e1
```

---

```{r n2o80cm, message=FALSE, warning=FALSE}
  e2 <- ggplot(n2o80, 
              aes(x=Sampled,
                  y=flux))
  e2 <- e2 + 
        geom_boxplot(fill="blue", alpha=0.2) + 
          ggtitle("N2O, Level 80cm") +
          labs(x="Sampling Dates", y="N2O flux") +
          theme(plot.title = element_text(family = "Trebuchet MS", color="#666666", face="bold", size=18, hjust=0)) +
          theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
          scale_y_continuous(name="flux in myg/m-2 h-1", limits=c(0, 20)) 
```

--- 

```{r, warning=FALSE}
  e2
```

---

```{r}
  e3 <- ggplot(n2o170, 
              aes(x=Sampled,
                  y=flux))
  e3 <- e3 + 
        geom_boxplot(fill="blue", alpha=0.2) + 
          ggtitle("N2O, Level 180cm") +
          labs(x="Sampling Dates", y="N2O flux") +
          theme(plot.title = element_text(family = "Trebuchet MS", color="#666666", face="bold", size=18, hjust=0)) +
          theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
          scale_y_continuous(name="flux in myg/m-2 h-1", limits=c(0, 20)) 
```

---

```{r, warning=FALSE}
  e3
```

---

## Multiplot Plot N2O Fluxes from Experimental Sites somehow produces S***

---


```{r, warning=FALSE}
    library(gridExtra)
    library(grid)
   grid.arrange(e1, e2, e3, ncol=3)
```

---

## N2O Boxplots from Control Site, no control spots, Level 0/80/170 cm

--- 

```{r}
  c1 <- ggplot(n2o0c, 
              aes(x=Sampled,
                  y=flux))
  c1 <- c1 + 
        geom_boxplot(fill="blue", alpha=0.2) + 
          ggtitle("Control site: N2O in myg/m-2 h-1, Level 0cm") +
          labs(x="Sampling Dates", y="N2O flux") +
          theme(plot.title = element_text(family = "Trebuchet MS", color="#666666", face="bold", size=18, hjust=0)) +
          theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
          scale_y_continuous(name="flux in", limits=c(0, 20)) 
```

---

```{r, warning=FALSE}
  c1
```

---

```{r}
  c2 <- ggplot(n2o80c, 
              aes(x=Sampled,
                  y=flux))
  c2 <- c2 + 
        geom_boxplot(fill="blue", alpha=0.2) + 
          ggtitle("Control site: N2O in  myg/m-2 h-1, Level 80cm") +
          labs(x="Sampling Dates", y="N2O flux") +
          theme(plot.title = element_text(family = "Trebuchet MS", color="#666666", face="bold", size=18, hjust=0)) +
          theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
          scale_y_continuous(name="flux in", limits=c(0, 20)) 
```

---

```{r, warning=FALSE}
  c2
```

---

```{r}
  c3 <- ggplot(n2o170c, 
              aes(x=Sampled,
                  y=flux))
  c3 <- c3 + 
        geom_boxplot(fill="blue", alpha=0.2) + 
          ggtitle("Control site: N2O in myg/m-2 h-1, Level 180cm") +
          labs(x="Sampling Dates", y="N2O flux") +
          theme(plot.title = element_text(family = "Trebuchet MS", color="#666666", face="bold", size=18, hjust=0)) +
          theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
          scale_y_continuous(name="flux in", limits=c(0, 20)) 
```

---
```{r, warning=FALSE}
  c3
```

---


## Still try to implement the three treem stem levels output into one plot


---

# TODOS

- one plot per level, each per experiment and control sites
- Plots according to extra data: humidity and temperature, regression
- Check the statistical relevance
- Normal distribution (Shapirov)

--- 

# Normal Distribution ?
 
---

```{r}
shapiro.test(n2o0$flux)
```

---

## Normal distribution assumed.

---

# Extra Tests with CH4

--- 

## Data Import,
Select my file and read data into 'dat' dataframe
File contains N20 fluxes for the SummerSchool irrigation experiment only.
For extended time slots, another file (see below) will be used.

--- 
```{r}
ch4<- read.csv("ch4R.csv", header = TRUE)
```

---

```{r}
ch4
```

---

## Check Table View

---

```{r}
  head(ch4)
```

---

## Data are still in wrong format (wide instead of long)

Thus, original data table needs to be converted /gathered - library 'tidyr' to be added to library list at the beginning

The arguments to gather():
 - data: Data object
 - key: Name of new key column (made from names of data columns)
 - value: Name of new value column
 - ...: Names of source columns that contain values
 - factor_key: Treat the new key column as a factor (instead of character vector)

---

## Re-Organising Data Colums, experimental sites

Zero level, experimental site
```{r}
  ch40 <- gather(ch4, "olevel", "flux", Tree1h0:Tree12h0, factor_key=TRUE)
ch40
```

---

80cm Level, experimental site
```{r}
  ch480 <- gather(ch4, "80level", "flux", Tree2h80:Tree12h80, factor_key=TRUE)
```

---

```{r}
ch480

```

---

170cm Level, experimental site
```{r}
  ch4170 <- gather(ch4, "170level", "flux", Tree2h170:Tree12h170, factor_key=TRUE)
```

---

```{r}
ch4170
```

---

## Re-Organising Data Colums, control sites

---

```{r}
  ch40c <- gather(ch4, "olevelC", "flux", Tree9h0:Tree11h0, factor_key=TRUE)
```

---

```{r}
ch40c
```

---

80cm Level, experimental site
```{r}
  ch480c <- gather(ch4, "80levelC", "flux", Tree9h80:Tree11h80, factor_key=TRUE)
```

---

```{r}
ch480c
```

---

170cm Level, experimental site
```{r}
  ch4170c <- gather(ch4, "170levelC", "flux", Tree9h170:Tree11h170, factor_key=TRUE)
```

---

```{r}
ch4170c
```

---

## CH4 Boxplots from Experimental Site, no control spots, Level 0/80/170 cm

```{r}
  ch1 <- ggplot(ch40, 
              aes(x=Sampled,
                  y=flux))
  ch1 <- ch1 + 
        geom_boxplot(fill="blue", alpha=0.2) + 
          ggtitle("CH4, Level 0cm") +
          labs(x="Sampling Dates", y="CH4 flux") +
          theme(plot.title = element_text(family = "Trebuchet MS", color="#666666", face="bold", size=18, hjust=0)) +
          theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
          scale_y_continuous(name="flux in myg/m-2 h-1", limits=c(0, 20)) 
```

---

```{r, warning=FALSE}
ch1
```

---

```{r}
  ch2 <- ggplot(ch480, 
              aes(x=Sampled,
                  y=flux))
  ch2 <- ch2 + 
        geom_boxplot(fill="blue", alpha=0.2) + 
          ggtitle("CH4, Level 80cm") +
          labs(x="Sampling Dates", y="CH4 flux") +
          theme(plot.title = element_text(family = "Trebuchet MS", color="#666666", face="bold", size=18, hjust=0)) +
          theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
          scale_y_continuous(name="flux in myg/m-2 h-1", limits=c(0, 20)) 
```

---

```{r, warning=FALSE}
  ch2
```

---

```{r}
  ch3 <- ggplot(ch4170, 
              aes(x=Sampled,
                  y=flux))
  ch3 <- ch3 + 
        geom_boxplot(fill="blue", alpha=0.2) + 
          ggtitle("CH4, Level 180cm") +
          labs(x="Sampling Dates", y="CH4 flux") +
          theme(plot.title = element_text(family = "Trebuchet MS", color="#666666", face="bold", size=18, hjust=0)) +
          theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
          scale_y_continuous(name="flux in myg/m-2 h-1", limits=c(0, 20)) 
```

---
```{r, warning=FALSE}
  ch3
```

---

## CH4 Boxplots from Control Site, no control spots, Level 0/80/170 cm

```{r}
  chc1 <- ggplot(ch40c, 
              aes(x=Sampled,
                  y=flux))
  chc1 <- chc1 + 
        geom_boxplot(fill="blue", alpha=0.2) + 
          ggtitle("Control site: CH4, Level 0cm") +
          labs(x="Sampling Dates", y="CH4 flux") +
          theme(plot.title = element_text(family = "Trebuchet MS", color="#666666", face="bold", size=18, hjust=0)) +
          theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
          scale_y_continuous(name="flux in myg/m-2 h-1", limits=c(0, 20)) 
```

---

```{r, warning=FALSE}
  chc1
```

---

```{r}
  chc2 <- ggplot(ch480c, 
              aes(x=Sampled,
                  y=flux))
  chc2 <- chc2 + 
        geom_boxplot(fill="blue", alpha=0.2) + 
          ggtitle("Control site: CH4, Level 80cm") +
          labs(x="Sampling Dates", y="CH4 flux") +
          theme(plot.title = element_text(family = "Trebuchet MS", color="#666666", face="bold", size=18, hjust=0)) +
          theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
          scale_y_continuous(name="flux in myg/m-2 h-1", limits=c(0, 5)) 
```

---
```{r, warning=FALSE}
chc2
```

---

```{r}
  chc3 <- ggplot(ch4170c, 
              aes(x=Sampled,
                  y=flux))
  chc3 <- chc3 + 
        geom_boxplot(fill="blue", alpha=0.2) + 
          ggtitle("Control site: CH4, Level 180cm") +
          labs(x="Sampling Dates", y="CH4 flux") +
          theme(plot.title = element_text(family = "Trebuchet MS", color="#666666", face="bold", size=18, hjust=0)) +
          theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
          scale_y_continuous(name="flux in myg/m-2 h-1", limits=c(0, 10)) 
```

---
```{r, warning=FALSE}
  chc3
```


# Extra Tests with CO2

--- 

## Data Import,
Select my file and read data into 'dat' dataframe
File contains CO2 fluxes for the SummerSchool irrigation experiment only.
For extended time slots, another file (see below) will be used.

--- 
```{r}
co2<- read.csv("co2R.csv", header = TRUE)
```

---

```{r}
co2
```

---

## Check Table View

---

```{r}
  head(co2)
```

---

## Data are still in wrong format (wide instead of long)

Thus, original data table needs to be converted /gathered - library 'tidyr' to be added to library list at the beginning

The arguments to gather():
 - data: Data object
 - key: Name of new key column (made from names of data columns)
 - value: Name of new value column
 - ...: Names of source columns that contain values
 - factor_key: Treat the new key column as a factor (instead of character vector)

---

## Re-Organising Data Colums, experimental sites

Zero level, experimental site
```{r}
  co20 <- gather(co2, "olevel", "flux", Tree1h0:Tree12h0, factor_key=TRUE)
co20
```

---

80cm Level, experimental site
```{r}
  co280 <- gather(co2, "80level", "flux", Tree2h80:Tree12h80, factor_key=TRUE)
```

---

```{r}
co280

```

---

170cm Level, experimental site
```{r}
  co2170 <- gather(co2, "170level", "flux", Tree2h170:Tree12h170, factor_key=TRUE)
```

---

```{r}
co2170
```

---

## Re-Organising Data Colums, control sites

---

```{r}
  co20c <- gather(co2, "olevelC", "flux", Tree9h0:Tree11h0, factor_key=TRUE)
```

---

```{r}
co20c
```

---

80cm Level, experimental site
```{r}
  co280c <- gather(co2, "80levelC", "flux", Tree9h80:Tree11h80, factor_key=TRUE)
```

---

```{r}
co280c
```

---

170cm Level, experimental site
```{r}
  co2170c <- gather(co2, "170levelC", "flux", Tree9h170:Tree11h170, factor_key=TRUE)
```

---

```{r}
co2170c
```

---

## CO2 Boxplots from Experimental Site, no control spots, Level 0/80/170 cm

```{r}
  co21 <- ggplot(co20, 
              aes(x=Sampled,
                  y=flux))
  co21 <- co21 + 
        geom_boxplot(fill="blue", alpha=0.2) + 
          ggtitle("CO2mob, Level 0cm") +
          labs(x="Sampling Dates", y="CO2 flux") +
          theme(plot.title = element_text(family = "Trebuchet MS", color="#666666", face="bold", size=18, hjust=0)) +
          theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
          scale_y_continuous(name="flux in g/m-2 h-1", limits=c(0, 2)) 
```

---

```{r, warning=FALSE}
co21
```

---

```{r}
  co22 <- ggplot(co280, 
              aes(x=Sampled,
                  y=flux))
  co22 <- co22 + 
        geom_boxplot(fill="blue", alpha=0.2) + 
          ggtitle("CO2mob, Level 80cm") +
          labs(x="Sampling Dates", y="CO2 flux") +
          theme(plot.title = element_text(family = "Trebuchet MS", color="#666666", face="bold", size=18, hjust=0)) +
          theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
          scale_y_continuous(name="flux in g/m-2 h-1", limits=c(0, 2)) 
```

---

```{r, warning=FALSE}
  co22
```

---

```{r}
  co23 <- ggplot(co2170, 
              aes(x=Sampled,
                  y=flux))
  co23 <- co23 + 
        geom_boxplot(fill="blue", alpha=0.2) + 
          ggtitle("CO2mob, Level 180cm") +
          labs(x="Sampling Dates", y="CO2 flux") +
          theme(plot.title = element_text(family = "Trebuchet MS", color="#666666", face="bold", size=18, hjust=0)) +
          theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
          scale_y_continuous(name="flux in g/m-2 h-1", limits=c(0, 2)) 
```

---
```{r, warning=FALSE}
  co23
```

---

## CO2 Boxplots from Control Site, no control spots, Level 0/80/170 cm

```{r}
  co2c1 <- ggplot(co20c, 
              aes(x=Sampled,
                  y=flux))
  co2c1 <- co2c1 + 
        geom_boxplot(fill="blue", alpha=0.2) + 
          ggtitle("Control site: CO2mob, Level 0cm") +
          labs(x="Sampling Dates", y="CO2 flux") +
          theme(plot.title = element_text(family = "Trebuchet MS", color="#666666", face="bold", size=18, hjust=0)) +
          theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
          scale_y_continuous(name="flux in g/m-2 h-1", limits=c(0, 2)) 
```

---

```{r, warning=FALSE}
  co2c1
```

---

```{r}
  co2c2 <- ggplot(co280c, 
              aes(x=Sampled,
                  y=flux))
  co2c2 <- co2c2 + 
        geom_boxplot(fill="blue", alpha=0.2) + 
          ggtitle("Control site: CO2mob, Level 80cm") +
          labs(x="Sampling Dates", y="CO2 flux") +
          theme(plot.title = element_text(family = "Trebuchet MS", color="#666666", face="bold", size=18, hjust=0)) +
          theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
          scale_y_continuous(name="flux in g/m-2 h-1", limits=c(0, 1)) 
```

---
```{r, warning=FALSE}
co2c2
```

---

```{r}
  co2c3 <- ggplot(co2170c, 
              aes(x=Sampled,
                  y=flux))
  co2c3 <- co2c3 + 
        geom_boxplot(fill="blue", alpha=0.2) + 
          ggtitle("Control site: CO2mob, Level 180cm") +
          labs(x="Sampling Dates", y="CO2 flux") +
          theme(plot.title = element_text(family = "Trebuchet MS", color="#666666", face="bold", size=18, hjust=0)) +
          theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
          scale_y_continuous(name="flux in g/m-2 h-1", limits=c(0, 1)) 
```

---
```{r, warning=FALSE}
  co2c3
```

---

## N2O AT NIGHT NOW !!!

---

```{r}
n2on <- read.csv("n2on.csv", header = TRUE)
```

---
```{r}
n2on
```

---

### Re-Organising Data Colums, experimental sites

Zero level, experimental site
```{r, echo=TRUE}
  n2on0 <- gather(n2on, "olevel", "flux", Tree1h0:Tree12h0, factor_key=TRUE)
```

---

```{r}
n2on0
```

---

80cm Level, experimental site
```{r}
  n2on80 <- gather(n2on, "80level", "flux", Tree2h80:Tree12h80, factor_key=TRUE)
```

--- 
```{r}
n2on80
```

---

170cm Level, experimental site
```{r}
  n2on170 <- gather(n2on, "170level", "flux", Tree2h170:Tree12h170, factor_key=TRUE)
```

---

```{r}
n2on170
```

---

## Re-Organising Data Colums, control sites

```{r}
  n2on0c <- gather(n2on, "olevelC", "flux", Tree9h0:Tree11h0, factor_key=TRUE)
```

---

```{r}
n2on0c
```

---

80cm Level, experimental site
```{r}
  n2on80c <- gather(n2on, "80levelC", "flux", Tree9h80:Tree11h80, factor_key=TRUE)
```

---

```{r}
  n2on80c
```

---

170cm Level, experimental site
```{r}
  n2on170c <- gather(n2on, "170levelC", "flux", Tree9h170:Tree11h170, factor_key=TRUE)
```

---

```{r}
n2on170c
```

---

## ! Data now look much better

---

## N2O Night Boxplots from Experimental Site, no control spots, Level 0/80/170 cm

---

```{r}
  n1 <- ggplot(n2on0, 
              aes(x=Sampled,
                  y=flux))
  n1 <- n1 + 
        geom_boxplot(fill="blue", alpha=0.2) + 
          ggtitle("N2O Night, Level 0cm") +
          labs(x="Sampling Dates", y="N2O flux") +
          theme(plot.title = element_text(family = "Trebuchet MS", color="#666666", face="bold", size=18, hjust=0)) +
          theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
          scale_y_continuous(name="flux in myg/m-2 h-1", limits=c(0, 20)) 
```

---

```{r, warning=FALSE}
  n1
```

---

```{r n2on80cm, message=FALSE, warning=TRUE}
  n2 <- ggplot(n2on80, 
              aes(x=Sampled,
                  y=flux))
  n2 <- n2 + 
        geom_boxplot(fill="blue", alpha=0.2) + 
          ggtitle("N2O Night, Level 80cm") +
          labs(x="Sampling Dates", y="N2O flux") +
          theme(plot.title = element_text(family = "Trebuchet MS", color="#666666", face="bold", size=18, hjust=0)) +
          theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
          scale_y_continuous(name="flux in myg/m-2 h-1", limits=c(0, 20)) 
```

--- 

```{r, warning=FALSE}
  n2
```

---

```{r}
  n3 <- ggplot(n2on170, 
              aes(x=Sampled,
                  y=flux))
  n3 <- n3 + 
        geom_boxplot(fill="blue", alpha=0.2) + 
          ggtitle("N2O night, Level 180cm") +
          labs(x="Sampling Dates", y="N2O flux") +
          theme(plot.title = element_text(family = "Trebuchet MS", color="#666666", face="bold", size=18, hjust=0)) +
          theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
          scale_y_continuous(name="flux in myg/m-2 h-1", limits=c(0, 20)) 
```

---

```{r, warning=FALSE}
  n3
```

---

## Multiplot Plot N2O NIGHT Fluxes from Experimental Sites somehow produces S***

---

```{r, warning=FALSE}
    library(gridExtra)
    library(grid)
   grid.arrange(n1, n2, n3, ncol=3)
```

---

## N2O Boxplots NIGHT from Control Site, no control spots, Level 0/80/170 cm

--- 

```{r}
  nn1 <- ggplot(n2on0c, 
              aes(x=Sampled,
                  y=flux))
  nn1 <- nn1 + 
        geom_boxplot(fill="blue", alpha=0.2) + 
          ggtitle("Control site: N2O Night, Level 0cm") +
          labs(x="Sampling Dates", y="N2O flux") +
          theme(plot.title = element_text(family = "Trebuchet MS", color="#666666", face="bold", size=18, hjust=0)) +
          theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
          scale_y_continuous(name="flux in myg/m-2 h-1", limits=c(0, 20)) 
```

---

```{r, warning=TRUE}
  nn1
```

---

```{r}
  nn2 <- ggplot(n2on80c, 
              aes(x=Sampled,
                  y=flux))
  nn2 <- nn2 + 
        geom_boxplot(fill="blue", alpha=0.2) + 
          ggtitle("Control site: N2O Night, Level 80cm") +
          labs(x="Sampling Dates", y="N2O flux") +
          theme(plot.title = element_text(family = "Trebuchet MS", color="#666666", face="bold", size=18, hjust=0)) +
          theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
          scale_y_continuous(name="flux inmyg/m-2 h-1", limits=c(0, 20)) 
```

---

```{r, warning=TRUE}
  nn2
```

---

```{r}
  nn3 <- ggplot(n2on170c, 
              aes(x=Sampled,
                  y=flux))
  nn3 <- nn3 + 
        geom_boxplot(fill="blue", alpha=0.2) + 
          ggtitle("Control site: N2O Night, Level 180cm") +
          labs(x="Sampling Dates", y="N2O flux") +
          theme(plot.title = element_text(family = "Trebuchet MS", color="#666666", face="bold", size=18, hjust=0)) +
          theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
          scale_y_continuous(name="flux in myg/m-2 h-1", limits=c(0, 20)) 
```

---
```{r, warning=TRUE}
  nn3
```

---
